\noindent \textbf{Paper Submission Checklist (place after references)}

\noindent \textbf{Student Name: } \newline
\noindent \textbf{Peer Reviewer Name: }  \newline
\noindent \textbf{Paper Title: } \newline
\noindent \textbf{Date: } \newline



%%% BEGIN INSTRUCTIONS %%%
This checklist should be at the front of every paper you submit for Sandeep's review. 
For each question, change the default \answerTODO{} to \answerYes{},
\answerNo{}, or \answerNA{}. It is OK if preliminary drafts have a few no's, but mark that carefully so its clear you will add that in.

%%% END INSTRUCTIONS %%%

\begin{enumerate}

\item For all student authors ...
\begin{enumerate}
    \item Did you spell check and grammar check the full document, using Grammarly if needed?
    \answerTODO{}
    \item Did you organize the LaTeX files according to the sample paper guide, including naming the file appropriately, organizing sections etc.? \answerTODO{}
  \item Did you make sure all plots are legible, in at least 20 point font, and ideally use the lab plotting tools/guidelines? \answerTODO{}
  \item Did you have another student in the lab peer review your paper for clarity, typos, wrong notation etc.? Send an email to Sandeep (CC'ing both students) with the paper draft. \answerTODO{}
  \item Did you make sure all references have the book/conference venue, not just the author and title? \answerTODO{}
  \item Did you use the common reference files in the lab GIT, making sure to put our internal papers in ref/SwarmLabPubs.bib and all other papers in ref/external.bib? \answerTODO{}
  \item Did you outline your paper and place the DARPA Heilmeier Catechism question answers at the top of the outline? \answerTODO{}
\end{enumerate}

\end{enumerate}
